Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-20 code/plots.Rmd
plots.Rmd modified to create some figures, added a figure top manuscript

```{r}
p1 <- all_sim |> 
  group_by(rep, type) |>
  filter(rep == 0) |>
  ggplot(aes(t, abundance, col = species)) + 
    geom_line()  + 
    facet_wrap(~type) + 
    labs(y = "reward", x = "repetition")

>>>>

```{r}
all_sim |> 
  group_by(rep, type) |>
  filter(rep == 0) |>
  ggplot(aes(t, abundance, col = species)) + 
    geom_line()  + 
    facet_wrap(~type) + 
    labs(y = "reward", x = "repetition")
all_sim |>
    group_by(rep,type) |>
    filter(rep<10) |>
    ggplot(aes(t, action)) + 
    geom_line()  + 
    facet_wrap(~type) + 
    labs(y = "action", x = "repetition")

### 2023-01-20 manuscript/manuscript.Rmd
plots.Rmd modified to create some figures, added a figure top manuscript

header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lineno}
  - \usepackage{setspace}
  - \usepackage{bookmark}
  - \usepackage{float}
  - \linenumbers
  - \doublespacing

@@

Our results suggest that DRL can find solutions that are more sustainable *and* more profitable than both MSY and TAC.
Indeed, DRL finds solutions in which, for certain periods of time, no harvest is performed on the system.
These periods effectively allow the system to, in a sense, ‘‘reset’’ itself.
They lead to a distinctive oscillating behavior of the system state over time, with periods of relative depletion followed by periods of growth. 
Figure \ref{fig:tbd} exemplifies this point by comparing the harvest effort and state times series obtained from these policies.

>>>>

header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lineno}
  - \usepackage{setspace}
  - \usepackage{bookmark}
  - \usepackage{float}
  - \usepackage{graphicx}
  - \linenumbers
  - \doublespacing

@@

Our results suggest that DRL can find solutions that are more sustainable *and* more profitable than both MSY and TAC.
Indeed, DRL finds solutions in which, for certain periods of time, no harvest is performed on the system.
These periods effectively allow the system to, in a sense, ‘‘reset’’ itself.
They lead to a distinctive oscillating behavior of the system state over time, with periods of relative depletion followed by periods of growth. 
Figure \ref{fig:tbd} exemplifies this point by comparing one times series of the system state obtained using each of these policies.

\begin{figure}
	\includegraphics[width=\linewidth]{Figures/timeseries.png}
\caption{
\label{fig:one timeseries}
tbd
}
\end{figure}
